### 2020-04-05 Thesis-Glossary.tex
Work on the introduction
Work on background; rearrange sections a bit

\newcommand{\newterm}[3]{
    \newglossaryentry{#1}{
        name={#2},
        description={#3}
    }
}
\newcommand{\term}{\ac}

@@

% NOTE: Do not end with a period. The package adds this for you.
% TODO: auto-update glossary.md. This should be the master, because it is more fully specified

@@

\newterm{horsemen}{The Four Horsemen}{
    Four reasons that governments and law enforcement agencies use to undercut public support for strong encryption. The
    four horsemen are terrorists, pedophiles (child pornographers), drug dealers (and traffickers), and money launderers
    (or kidnappers)
}

\newterm{horsemen-full}{The Four Horsemen of the Infocalypse}{
    The long name for ``The Four Horsemen''
}
% End terms

@@

% Start acronyms
\newabbreviation{AECA}{AECA}{Arms Export Control Act}
\newabbreviation{AV}{AV}{anti-virus}
\newabbreviation{AWA}{AWA}{All Writs Act}
\newabbreviation{CALEA}{CALEA}{Communications Assistance for Law Enforcement Act}
\newabbreviation{CFAA}{CFAA}{Computer Fraud and Abuse Act}
\newabbreviation{CP}{CP}{child pornography}
\newabbreviation{CSAM}{CSAM}{child sexual abuse material}
\newabbreviation{DE}{DE}{device encryption}
\newabbreviation{DIM}{DIM}{data in motion}
\newabbreviation{DAR}{DAR}{data at rest}
\newabbreviation{E2E}{E2E}{end to end}
\newabbreviation{EA}{EA}{exceptional (or extraordinary) access}
\newabbreviation{ECPA}{ECPA}{Electronic Communications Privacy Act}
\newabbreviation{ED}{ED}{ephemeral data}
\newabbreviation{FBI}{FBI}{Federal Bureau of Investigation}
\newabbreviation{FISA}{FISA}{Foreign Intelligence Surveillance Act}
\newabbreviation{FISAAA}{FISAAA}{FISA Amendments Act}
\newabbreviation{FISC}{FISC}{Foreign Intelligence Surveillance Court}
\newabbreviation{ITAR}{ITAR}{International Traffic in Arms Regulations}
\newabbreviation{KEK}{KEK}{key encrypting key}
\newabbreviation{LE}{LE}{law enforcement}
\newabbreviation{LEA}{LEA}{law enforcement agency}
\newabbreviation{LEO}{LEO}{law enforcement officer}
\newabbreviation{NED}{NED}{non-ephemeral data}
\newabbreviation{NSA}{NSA}{National Security Agency}
\newabbreviation{NSL}{NSL}{National Security Letter}
\newabbreviation{PAA}{PAA}{Protect America Act}
\newabbreviation{PGP}{PGP}{Pretty Good Privacy}
\newabbreviation{PIN}{PIN}{personal identification number}
\newabbreviation{PKI}{PKI}{public key infrastructure}
\newabbreviation{PW}{PW}{password}
\newabbreviation{SE}{SE}{strong encryption}
\newabbreviation{SSO}{SSO}{single sign-on}
\newabbreviation{TLS}{TLS}{Transport Layer Security}
\newabbreviation{VPN}{VPN}{virtual private network}
% End acronyms

>>>>

\newcommand{\newterm}[3]{
    \newglossaryentry{#1}{
        name={#2},
        description={#3}
    }
}
\newcommand{\term}{\ac}
\newcommand{\Term}{\Ac}

@@

% NOTE: Do not end with a period. The package adds this for you.
% IDEA: auto-update glossary.md. This should be the master, because it is more fully specified

@@

\newterm{horsemen}{the Four Horsemen}{
    Four reasons that governments and law enforcement agencies use to undercut public support for strong encryption. The
    four horsemen are terrorists, pedophiles (child pornographers), drug dealers (and traffickers), and money launderers
    (or kidnappers)
}
\newterm{horsemen-full}{The Four Horsemen of the Infocalypse}{The long name for ``The Four Horsemen''}

\newterm{plaintext}{plaintext}{Unencrypted data}
\newterm{ciphertext}{ciphertext}{Encrypted data}

\newterm{cryptography}{cryptography}{
    The study of techniques for communicating secretly in the presence of third parties
}

\newterm{cipher}{cipher}{
    A tool or algorithm to perform encryption, translating between plaintext and ciphertext
}
\newterm{key}{key}{Secret information required to operate the cipher and perform encryption and decryption}

\newterm{encryption}{encryption}{The process of translating from plaintext to ciphertext}
\newterm{decryption}{decryption}{The process of translating from ciphertext to plaintext}

\newterm{public-key-crypto}{public key cryptography}{
    Another name for asymmetric encryption
}
\newterm{asym-crypto}{asymmetric cryptography}{
    A cipher scheme where encryption and decryption are performed with separate, paired keys, called the public key and
    the private key
}
\newterm{sym-crypto}{symmetric cryptography}{
    A cipher scheme where encryption and decryption are performed with the same key
}
% End terms

@@

% Start acronyms
\newabbreviation{AECA}{AECA}{Arms Export Control Act}
\newabbreviation{AV}{AV}{anti-virus}
\newabbreviation{AWA}{AWA}{All Writs Act}
\newabbreviation{CALEA}{CALEA}{Communications Assistance for Law Enforcement Act}
\newabbreviation{CFAA}{CFAA}{Computer Fraud and Abuse Act}
\newabbreviation{CP}{CP}{child pornography}
\newabbreviation{CSAM}{CSAM}{child sexual abuse material}
\newabbreviation{DE}{DE}{device encryption}
\newabbreviation{DIM}{DIM}{data in motion}
\newabbreviation{DAR}{DAR}{data at rest}
\newabbreviation{E2E}{E2E}{end to end}
\newabbreviation{EA}{EA}{exceptional access}
\newabbreviation{ECPA}{ECPA}{Electronic Communications Privacy Act}
\newabbreviation{ED}{ED}{ephemeral data}
\newabbreviation{FBI}{FBI}{Federal Bureau of Investigation}
\newabbreviation{FISA}{FISA}{Foreign Intelligence Surveillance Act}
\newabbreviation{FISAAA}{FISAAA}{FISA Amendments Act}
\newabbreviation{FISC}{FISC}{Foreign Intelligence Surveillance Court}
\newabbreviation{ITAR}{ITAR}{International Traffic in Arms Regulations}
\newabbreviation{KEK}{KEK}{key encrypting key}
\newabbreviation{LE}{LE}{law enforcement}
\newabbreviation{LEA}{LEA}{law enforcement agency}
\newabbreviation{LEO}{LEO}{law enforcement officer}
\newabbreviation{NED}{NED}{non-ephemeral data}
\newabbreviation{NSA}{NSA}{National Security Agency}
\newabbreviation{NSL}{NSL}{National Security Letter}
\newabbreviation{PAA}{PAA}{Protect America Act}
\newabbreviation{PGP}{PGP}{Pretty Good Privacy}
\newabbreviation{PIN}{PIN}{personal identification number}
\newabbreviation{PKI}{PKI}{public key infrastructure}
\newabbreviation{PW}{PW}{password}
\newabbreviation{SE}{SE}{strong encryption}
\newabbreviation{SSO}{SSO}{single sign-on}
\newabbreviation{TLS}{TLS}{Transport Layer Security}
\newabbreviation{VPN}{VPN}{virtual private network}
% End acronyms
